The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction

### 2024-02-14 outputs/paper/paper.qmd
some more edits

Utilizing the same dataset and a similar methodology to Feldman et al. (2017), we aim to replicate their results in the context of the United States, a very heterogenous country that is characterized by a high importance of individualist, but also cultural diversity and socioeconomic inequality. While Feldman et al. did investigate the relationship between the belief in free will and job satisfaction in the United States, they did not integrate these results to the cross-cultural analysis, as the US were not included in the sample of 16 countries. This paper, therefore, seeks to fill this gap and reproduce these aspects of the Feldman et al. paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national-level, using the World Values Survey. The estimand is the correlation between the belief in free will and job satisfaction. Our reproduction was conducted using the statistical programming language R (@citeR). In the data analysis and visualization process, we also made use of the following R packages: tidyverse (@citetidyverse), dplyr (@citedplyr), knitr (@citeknitr), kableExtra (@citekExtra), and countrycode (@citecc).

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

Talk way more about it.

>>>>

Utilizing the same dataset and a similar methodology to Feldman et al. (2017), we aim to replicate their results in the context of the United States, a very heterogenous country that is characterized by a high importance of individualist, but also cultural diversity and socioeconomic inequality. While Feldman et al. did investigate the relationship between the belief in free will and job satisfaction in the United States, they did not integrate these results to the cross-cultural analysis, as the US were not included in the sample of 16 countries. This paper, therefore, seeks to fill this gap and reproduce these aspects of the Feldman et al. paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national-level, using the World Values Survey. We will also consider whether there are any significant differences between the national-level data and the Amazon Mechanical Turk data. The estimand is the correlation between the belief in free will and job satisfaction. Our reproduction was conducted using the statistical programming language R (@citeR). In the data analysis and visualization process, we also made use of the following R packages: tidyverse (@citetidyverse), dplyr (@citedplyr), knitr (@citeknitr), kableExtra (@citekExtra), and countrycode (@citecc).

@@

# Results {#sec-results}
A173 free will
c033 job satisfaction
c034 decisions in the job
F198 Fate versus control
G023 autonomous individual
C031 degree of pride in your work
X003 Age
X001 Sex
